---
title: "Support Us"
theme: theme.css
footer: _footer.html
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Potential Corporate Sponsors
The "NUTS!" would be happy to start a partnership at any level! Our total cost to participate in the World Championship is $20,000, but we would welcome any contribution towards that goal. If you are willing and able to help, please reach out to us at summum6133@gmail.com or send a check to the Walnut Hills Alumni Foundation 3250 Victory Pkwy, Cincinnati, OH 45207, earmarked for FTC Robotics. Your tax-deductible contribution will bring us one step closer to the FTC World Championship! 

## Donors
Please consider donating to our **[GoFundMe](https://gofund.me/a6ca5908)** to support our trip to the [FTC World Championship](https://www.firstchampionship.org/).
100% of fundraising for the trip will be used for:

- Team, coach, and parent chaperone travel (airline tickets)

- Extra baggage and shipping fees for robotics equipment

- Van rental in Houston

- Team, coach, and parent chaperone lodging costs

- Team, coach, and parent chaperone meals


## Current Sponsors
Thank you to all of our 2022-23 Season Sponsors for making our amazing season possible!

```{r currentSponsors, out.width = "500px"}
htmltools::includeHTML("currentSponsors.html")
```

